Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massively Distributed Evolutionary Computation

### 2015-07-30 volunteer-clouds-ieee-ci-si.tex
some comments
Partial improvement

% [Pedro] no aparecía el primer autor. En cualquier caso, lo dejo comentado a continuación.

@@

% [Pedro] Alternativa para poner los autores. Ahora sí los muestra correctamente.

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Volunteer computing is used routinely in science and industry, but it
still has a long way to go if it is going to become mainstream in the
same way the cloud technologies in general have. The lack of general purpose tools
with analytics built in could be one of the reasons why this is so, as
well as the lack of proofs of concept. That is why in this paper we
present NodIO, a client-server architecture for distributed
evolutionary algorithms, written entirely in JavaScript, which needs
minimal server support to work and is able to support persistent,
asynchronous, distributed evolutionary algorithms running in the
browser. The architecture, along with some initial results on the expected performance and scaling
behavior is presented. We also use the algorithm analytics to try and  %[Pedro] I don't understand what "the algorithm analytics" stand for???
create a model of user behavior which, as is usual in this kind of
computing models, follow a Weibull distribution. 
\end{abstract}

@@

%---------------------------------------------------------------
\section{Introduction}

@@

There is, then, space for systems that do not have any of those
assumptions, such as the one presented in this paper, which will be
provisionally named {\sf NodIO}. NodIO is first an application that
runs in two tiers, a server and a client that can be possibly run on a  % [Pedro] Both the server and the client in browsers? different browsers as I understand?
browser. As such, it can be run in any computer that loads the web
page where the client is embedded, including possibly many over which
the scientist has no control.

When faced with the problem of diminishing funds for buying new     % [Pedro] This sentence is so so long. I would split it in two sentences.
hardware and continuous hardware failures of existing clusters and
taking into account our experience of working with web applications,
including JavaScript, from the beginning and other volunteer and
unconventional distributed evolutionary computing systems, our group
decided to create a new free framework that would allow anyone to
create a volunteer distributed EC experiment using cloud resources as
servers and browsers as clients.

@@

The rest of the paper is organized as follows: Next we present the
state of the art (Section \ref{sec:soa}) in web-based distributed 
computation systems along with attempts to predict and model its behavior. 
Then, a detailed description of the proposed system is presented 
in Section \ref{sec:description}, followed by the experiments and 
obtained results in Section \ref{sec:experiments}.
Finally, conclusions and future work are presented in Section \ref{sec:conclusion}.

%---------------------------------------------------------------
\section{State of the art}
\label{sec:soa}

@@

%---------------------------------------------------------------
\section{Description of the system}
\label{sec:description}

%---------------------------------------------------------------
\section{Experiments and obtained results}
\label{sec:experiments}

%---------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

The conclusion goes here.

%---------------------------------------------------------------
% use section* for acknowledgment
\section*{Acknowledgment}

>>>>

@@

@@

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
Volunteer computing is used routinely in science and industry, but it
still has a long way to go if it is going to become mainstream in the
same way the cloud in general has. The lack of general purpose tools
with analytics built in could be one of the reasons why this is so, as
well as the lack of proofs of concept. That is why in this paper we
present NodIO, a client-server architecture for distributed
evolutionary algorithms, written entirely in JavaScript, which needs
minimal server support to work and is able to support persistent,
asynchronous, distributed evolutionary algorithms running in the
browser. The architecture, along with some initial results on the expected performance and scaling
behavior is presented. We also use the algorithm analytics to try and
create a model of user behavior which, as is usual in this kind of
computing models, follow a Weibull distribution. 
\end{abstract}

@@

\section{Introduction}

@@

There is, then, space for systems that do not have any of those
assumptions, such as the one presented in this paper, which will be
provisionally named {\sf NodIO}. NodIO is first an application that
runs in two tiers, a server and a client that can be possibly run on a
browser. As such, it can be run in any computer that loads the web
page where the client is embedded, including possibly many over which
the scientist has no control.

When faced with the problem of diminishing funds for buying new
hardware and continuous hardware failures of existing clusters and
taking into account our experience of working with web applications,
including JavaScript, from the beginning and other volunteer and
unconventional distributed evolutionary computing systems, our group
decided to create a new free framework that would allow anyone to
create a volunteer distributed EC experiment using cloud resources as
servers and browsers as clients.

@@

The rest of the paper is organized as follows. Next we present the
state of the art in web-based distributed computation systems along
with attempts to predict and model its behavior.

\section{State of the art}
\label{sec:soa}

@@

\section{Description of the system}

In general, a volunteer-based distributed evolutionary computation
system based on the browser is simply a client-server architecture
whose client is, or can be, embedded in the browser via
JavaScript. All parts of the system are free and available with a free
license from \url{https://github.com/JJ/splash-volunteer}.
Thus, {\sf NodIO} has two parts:\begin{enumerate}
\item A REST server, that is, a server that includes several remote
  requests for storing and retrieving information (the CRUD cycle:
  create, request, update and delete) from the server. The information
  is of two kinds: {\em problem} based, that is, related to the
  evolutionary algorithm such as {\tt PUT}ing a chromosome in or {\tt
    GET}ing a random chromosome from it. It also peforms logging
  duties, but is basically a very lightweight and hign performance
  data store \cite{jj:idc:lowcost}.
\item A client that includes the evolutionary algorithm as 
  JavaScript code embedded in a web page that displays graphs and some
  additional links and information on the experiment. This code runs
  an evolutionary algorithm {\em island} starting with random
  population and sending, every 100 generations, the best individual
  back to the server (via a {\tt PUT} request) and requesting a random
  individual from the server (via a {\tt GET} request).
\end{enumerate}

The researcher only has to change a function to solve a different
problem, in this case the classical Trap function has been
used. JavaScript is a functional language and

\section{Conclusion}
The conclusion goes here.

% use section* for acknowledgment
\section*{Acknowledgment}
